%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%%%%%%%%

%-------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[strict]{changepage}

\name{Yingkai Gao} % Your name
\address{kyle.ygao@gmail.com} % Your phone number and email

\begin{document}

%-------------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Bachelor of Science in Computer Science, Beihang University} \hfill {\em Sep.2010 - Present} \\
School of Computer Science \& Engineering \\
Weighted Average Score: 90.15/100 \textbf{Rank: 3/217}\\
{\bf Exchange Student, National University of Singapore} \hfill {\em Aug.2012 - Dec.2012} \\
School of Computing \hfill Supervised by Prof. Tat-Seng Chua \\
Cumulative Grade Average Point: 4.8/5 (graded A+, i.e. around \textbf{top 3\%}, in 2 out of 5 courses) \\
%{\bf Standardized Test: } TOEFL - 110 (Speaking: 24) GRE - V160(84\%),  Q170(98\%), AW4.0(54\%)

\end{rSection}

%-------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%-------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Microsoft Research Asia}{Apr.2013 - Jan.2014}{Internship mentored by Lead Researcher Yunbo Cao}{Knowledge Mining Group}
\item Proposed a weakly-supervised clustering framework to extract query intent templates, which can enable search engines to have a deeper understanding of web search queries, from real-world query logs. Guided by a small amount of labeled data, the framework can determine the number of new clusters while determining $K$ is a difficult problem in most clustering applications.
\end{rSubsection}

\begin{rSubsection}{NLP\&CC\footnote{NLP\&CC is short for Natural Language Processing and Chinese Computing Conference} 2012 Chinese Tweets Sentiment Evaluation}{Jun.2012 - Nov.2012}{Group Leader}{Institute of Intelligent Information, Beihang University}
\item Won \textbf{1st} place of 53 entries in opinion detection task, and the \textbf{4nd} place in sentiment classification task.
\item Proposed a new word detection algorithm that \textbf{improves the precision in sentiment classification by 10\%.}
\item Developed the framework for Text Sentiment Evaluation with word segmentation, dependency parsing, named entity recognition, and other preprocessing components integrated.  Implemented the baseline system for comparison.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{NExT Search Center}{Aug.2012 - Dec.2012}{Part-time Developer}{School of Computing @ I Cube, National University of Singapore}
\item Implemented a module of a distributed real-time crawler by analyzing the layouts and structures of user generated content websites like Twitter, Amazon, and Flicker.  Developed a web service system for researchers to obtain and explore the crawled data in research experiments.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{National Student Innovation Program}{Dec.2011 - Present}{Leader}{Institute of Intelligent Information, Beihang University}
\item Proposed the research project named \emph {Sentiment Analysis in Social Network} as the \textbf{team leader} of a 5-member group.  Developed a prototype of web application on RenRen platform called Sentiment Roller Coaster.  The application analyzes the sentiment timeline of users by applying a SVM classifier on the contents posted by users.
\item Observing and analyzing the dynamic evolution of collective emotions in social networks, aiming to find regularities and patterns that can facilitate the sentiment analysis.
\item {\em This project is funded by National Student Innovation Program.}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{MicroStrategy}{Jun.2012 - July.2012}{Intern Software Engineer}{Beijing, China}
\item Developed a web service system for large-scale e-commerce transaction.
\end{rSubsection}

\end{rSection}

\pagebreak[4]

\begin{rSection}{Working Paper}
\textbf{Yingkai Gao}, Xin Zhao, Yunbo Cao. ``A weakly-supervised approach to mining of query intent templates on entity attributes"
\begin{adjustwidth}{8pt}{0pt}
 We try to express the intents about entity attributes by mining query intent templates from query log.  The mining process consists of two steps: (a) Automatically collect various expressions on attributes and (b) Group and ground the expressions to the attributes defined in a knowledge base.  We propose a framework that employs a weakly-supervised and metric learning integrated clustering method to construct query intent templates.
\end{adjustwidth}

\end{rSection}

%----------------------------------------------------------------------------------
%	Honors/Awards
%----------------------------------------------------------------------------------
\begin{rSection}{Honors\&Awards}
Microsoft Young Fellowship (Aug.2013) \\
\hspace*{8pt} - to the 36 best students from the 12 top universities in China \\
China Computer Federation Outstanding Student (Oct.2013) \\
\hspace*{8pt} - to the 100 best Computer Science students in China  \\
SAMSUNG Scholarship (Oct.2012) \\
\hspace*{8pt} - 1 out of 217 students in School of Computer Science and Engineering, Beihang University\\
National Scholarship (Oct.2011) \\
\hspace*{8pt} - 3 out of 217 students in School of Computer Science and Engineering, Beihang University\\
First Prize Scholarship for both academic records and cultural activities (Oct.2011) \\
\hspace*{8pt} - 2 out of 30 students \\
Innovative Prize (between first prize and second prize) of FengRu Cup for Students Scientific and Technological Practice (Mar.2011) \\
Best Photo Prize of 3rd World University Students Photographic Art Exhibition (Apr.2011) \\
First Prize of National Olympiad in Informatics in Provinces (Dec.2008)
\end{rSection}



%-------------------------------------------------------------------------------------
%	Qualities&Other Skills
%-------------------------------------------------------------------------------------

\begin{rSection}{Miscellaneous}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Teaching & Student Teacher at Secondary School of Programming in Beihang University \\
& \hspace{8pt}- taught basic algorithms and data structures for students not majoring in \\
& \hspace{8pt} computer science \\
Activities & Student member of ACM\&CCF \\
& Vice-President of the Student Union of the School of Computer Science and Engineering \\
& Volunteer Translator for TED\&Coursera \\
& Professional Photographers of America \\
& Amateur top level certificate of piano
\end{tabular}
\end{rSection}

%-------------------------------------------------------------------------------------

\end{document}
