%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	%%%%%%%%

%-------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.3in,right=0.5in,bottom=0.3in]{geometry} % Document margins
\usepackage[strict]{changepage}

\name{Yingkai (Kyle) Gao} % Your name
\address{Tel:412-892-0599 \quad Email:kyle.ygao@gmail.com} % Your phone number and email

\begin{document}

%-------------------------------------------------------------------------------------
%   Objective and Duration
%-------------------------------------------------------------------------------------
%{\bf Objective: } Research Software Engineer position that utilizes both my experience of Information
%Retrieval and my skills of software development and general computer science to make significant
%contribution to IBM. \\
%{\bf Estimated Start Time: } May, 2016
%-------------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Master of Language Technologies, Carnegie Mellon University} \hfill {Aug.2014 - Aug.2016} \\
Language Technologies Institute \hfill Advised by Jamie Callan \\
Courses: Search Engine, Machine Learning for Large Dataset/Text Mining, Intermediate Statistics \\
{\bf Bachelor of Science in Computer Science, Beihang University} \hfill {Sep.2010 - Jul.2014} \\
%School of Computer Science \& Engineering \\
Weighted Average Score: 90.15/100 \textbf{Rank: 3/217}\\
{\bf Exchange Student, National University of Singapore} \hfill {Aug.2012 - Dec.2012} \\
School of Computing \hfill Supervised by Tat-Seng Chua \\

\vspace{-2em} % shorten the space between two sections
\end{rSection}

%-------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%-------------------------------------------------------------------------------------

\begin{rSection}{Experience}
\begin{rSubsection}{Language Technologies Institute}{Aug.2014 - Present}{}{}
\item \textbf{EAGER Table Search}: This project explores through a prototype the possibility of non-textual data retrieval.
Tables from scientific publications were extracted and indexed for searching.  Studied novel representation and enrichment
for both document and query sides, explored user interface specifically for scientific search, and built a dataset with
careful user study.
\item \textbf{Entity Hierarchy Embedding}: This project enriches entity embedding by incorporating category hierarchy from Wikipedia.
Meaningful semantics are encoded to improves applications such as entity linking.
\end{rSubsection}

\begin{rSubsection}{Microsoft Research Asia}{Apr.2013 - Jan.2014}{}{}
\item Proposed a weakly-supervised clustering framework that (a) automatically collects various expressions on attributes from query log and 
(b) ground the expressions to the attributes defined in a knowledge base.
\item The framework was integrated into MS Bing's query understanding module to improve its user experience.
\end{rSubsection}

\begin{rSubsection}{NLP\&CC\footnote{NLP\&CC is short for Natural Language Processing and Chinese Computing Conference} 2012 Chinese Tweets Sentiment Evaluation}{Jun.2012 - Nov.2012}{}{}
\item I lead the project that won \textbf{1st} place of 53 entries in opinion detection task, \textbf{4nd} place in sentiment classification task.
Developed the framework for short text sentiment evaluation and implemented the baseline system for comparison.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{NExT Search Center}{Aug.2012 - Dec.2012}{}{}
\item Implemented a module of a distributed real-time crawler by analyzing the layouts and structures of user generated content websites like Twitter, Amazon, and Flicker, using Java and MongoDB.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{MicroStrategy}{Jun.2012 - July.2012}{}{}
\item Developed a web service system for large-scale e-commerce transaction, using Java and Spring Framework.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------
\begin{rSection}{Publications}
\begin{rSubsection}{}{}{}{}
\item Ongoing: Scientific Table Search Using Keyword Queries. Submitted to JCDL 2016.
\item Hu, Zhiting, Poyao Huang, Yuntian Deng, \textbf{Yingkai Gao}, and Eric P. Xing. ``Entity Hierarchy Embedding." ACL'2015.
%\item \textbf{Yingkai Gao}, Anran Wang, Xiang Wang, Chuanqi Tan, Lixuan Guo, Xiaoyuan Yang. ``Generalization and Application of Leibniz Formula and Integration by Parts."" Studies in College Mathematics. (2013):006.
\end{rSubsection}
\end{rSection}

\pagebreak[4]

%----------------------------------------------------------------------------------
%	Technical Skills
%----------------------------------------------------------------------------------
\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\hspace{6ex}\bfseries}l @{\hspace{6ex}} l }
Basic & Algorithms, Data Structure, Information Retrieval, Machine Learning \\
Language & Java, Python, C, Bash \\
Tool/Lib & ElasticSearch, Lucene, Hadoop, LightSVM, NumPy, IPython, Git
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------
%	Honors/Awards
%----------------------------------------------------------------------------------
\begin{rSection}{Honors\&Awards}
\begin{rSubsection}{}{}{}{}
\item Microsoft Young Fellowship - to the 36 best students from the 12 top universities in China
\item China Computer Federation Outstanding Student - to the 100 best Computer Science students in China
\item Best Photo Prize of 3rd World University Students Photographic Art Exhibition
\item National Scholarship
\item First Prize of National Olympiad in Informatics in Provinces 
\end{rSubsection}
\end{rSection}

\begin{rSection}{Miscellaneous}
\begin{rSubsection}{}{}{}{}
\item External reviewer for ICTIR'2016
\item Vice-President of Chinese Students and Scholars Association at CMU
\item Vice-Chair of CMU Summit on US-China Innovation and Entrepreneurship
\item Vice-President of the Student Union of the School of Computer Science and Engineering
\item Volunteer Translator for TED\&Coursera
\item Professional Photographers of America
\end{rSubsection}
\end{rSection}

\end{document}
